---
title: "Project Report"
author: "Jimmy Effendy"
date: "27/09/2021"
output: bookdown::pdf_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, echo=FALSE, warning=FALSE)
library(tidyverse)
library(ggplot2)
source("test-codes.R")
```

# Introduction

The aim of this project is to create a package that can produce figures that
are aesthetically cohesive for a textbook in an automatic and reproducible
manner. 

Firstly, the report will present two different figures styles/aesthetics. Next,
these proposed figures aesthetics will be compared against ggplot2 basic themes.

# theme_wombat

The first figure aesthetic variant is called `theme_wombat`. This theme is built 
upon ggplot2 basic theme `theme_bw`.

```{r wombat-scatter}
ggplot(mtcars, aes(mpg,disp,color=factor(carb))) + 
  geom_point(size=3) + 
  labs(title="Scatter Plot",
       subtitle = "disp vs mpg",
       caption = "Data: mtcars") +
  theme_wombat()+
  scale_colour_magpie()
```

```{r wombat-bar}
ggplot(mtcars, aes(factor(carb),fill=factor(carb))) + 
  geom_bar() + 
  scale_y_continuous(expand = c(0,0)) + 
  scale_x_discrete(expand = c(0,0)) +
  labs(title="Bar Plot") +
  theme_wombat()
```

```{r wombat-line}
ggplot(economics_long, aes(date, value01, colour = variable)) +
  geom_line() +
  scale_y_continuous(expand = c(0,0)) + 
  scale_x_continuous(expand = c(0,0)) +
  labs(title = "Line Plot",
       caption = "Data: economics_long") +
  theme_wombat()
```

```{r wombat-facet}
ggplot(data = mpg,aes(cty, hwy,color=class))+geom_point(size=3) + 
  facet_wrap(~ manufacturer,scales="free")+
  labs(title="Plot With Facets") + 
  theme_wombat() +
  scale_colour_magpie()
```

# theme_seagull

# Comparisons

# Currently in Development